### 2022-01-18 src-latex/main-paper.tex
Compress page 1

\begin{document}
%
\title{A Benchmark of Named Entity Recognition Approaches in Historical Documents\\
Application to 19$^{th}$ Century French Directories%
% FIXME "19$^{th}$-Century" with dash?
\thanks{This work was supported by the French National Research Agency:
Project SoDuCo, grant ANR-18-CE38-0013. ???FIXME need acknowledgments for directory sources???}}
%
\titlerunning{A Benchmark of NER Approaches in Historical Documents}
%
\author{%
Nathalie Abadie\inst{1}\orcidID{0000-0001-8741-2398} \and
Edwin Carlinet\inst{2}\orcidID{0000-0001-5737-5266} \and
Joseph Chazalon\inst{2}\orcidID{0000-0002-3757-074X} \and
Bertrand Duménieu\inst{3}\orcidID{0000-0002-2517-2058}\\
{\footnotesize \emph{all authors contributed equally}}%
}
%
\authorrunning{N. Abadie et al.}
%
\institute{%
% 1
LASTIG, Univ. Gustave Eiffel, IGN-ENSG, F-94160 Saint-Mandé, France\\
\email{nathalie-f.abadie@ign.fr}\\
\url{https://www.umr-lastig.fr/nathalie-abadie/} \and
% 2
EPITA Research \& Development Laboratory (LRDE), Le Kremlin-Bicêtre, France\\
\email{\{edwin.carlinet,joseph.chazalon\}@lrde.epita.fr}\\
\url{https://lrde.epita.fr} \and
% 3
CRH-EHESS, Paris, France\\
\email{bertrand.dumenieu@ehess.fr}\\
\url{http://crh.ehess.fr/index.php?5206}%
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{parts/00-abstract.tex}
\keywords{Historical documents \and Natural Language Processing \and Named Entity Recognition \and OCR noise \and Annotation cost.}
\end{abstract}

@@

\section*{Acknowledments}
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.

The authors want to thank \textcolor{green}{Laureencia for annotations, Guillaume Thomas for data processing? Stéphane Bacciochi and Pascal Cristofoli for helping to create the gold reference dataset ?}

>>>>

\begin{document}
%
\title{A Benchmark of Named Entity Recognition Approaches in Historical Documents\\
Application to 19$^{th}$ Century French Directories%
% FIXME "19$^{th}$-Century" with dash?
% \thanks{%
% This work was supported by the French National Research Agency:
% Project SoDuCo, grant ANR-18-CE38-0013.% ???FIXME need acknowledgments for directory sources???
% }
}
%
\titlerunning{A Benchmark of NER Approaches in Historical Documents}
%
\author{%
N. Abadie\inst{1}\orcidlink{0000-0001-8741-2398} \and
E. Carlinet\inst{2}\orcidlink{0000-0001-5737-5266} \and
J. Chazalon\inst{2}\orcidlink{0000-0002-3757-074X} \and
B. Duménieu\inst{3}\orcidlink{0000-0002-2517-2058}\\
{\footnotesize \emph{all authors contributed equally}}%
}
%
\authorrunning{N. Abadie et al.}
%
\institute{%
% 1
LASTIG, Univ. Gustave Eiffel, IGN-ENSG, F-94160 Saint-Mandé, France\\
\email{nathalie-f.abadie@ign.fr}%\\
% \url{https://www.umr-lastig.fr/nathalie-abadie/}%
\and
% 2
EPITA Research \& Development Laboratory (LRDE), Le Kremlin-Bicêtre, France\\
\email{\{edwin.carlinet,joseph.chazalon\}@lrde.epita.fr}%\\
%\url{https://lrde.epita.fr}
\and
% 3
CRH-EHESS, Paris, France\\
\email{bertrand.dumenieu@ehess.fr}%\\
% \url{http://crh.ehess.fr/index.php?5206}\\
\joseph{Je propose de supprimer les URLs.}%
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{parts/00-abstract.tex}
\keywords{Historical documents \and Natural Language Processing \and Named Entity Recognition \and OCR noise \and Annotation cost.}
\end{abstract}

@@

\section*{Acknowledgments}
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.

The authors want to thank Stéphane Bacciochi and Pascal Cristofoli for helping to create the gold reference dataset, 
Laureencia Maurice for annotating data,
as well as Guillaume Thomas, Paul Abi Saad, Raphaël Lelièvre, Dorian Mignon, Thibault Cavaciuti and Pierre Sadki for contributing to the annotation platform.
\joseph{On peut essayer de gagner de la place en déplaçant ça en footnote de 1ere page.}
